### 2023-05-30 paper/localpsf.tex
add advection diffusion convergence iterations table to paper

>>>>

\begin{figure}
	\begin{center}
		\begingroup
		\setlength{\tabcolsep}{8pt}
		\renewcommand{\arraystretch}{1.25}
		\begin{tabular}{c| c | c c c c c}
			& $\kappa$    & REG     &	NONE   & PSF $(1)$ & PSF $(5)$ & PSF $(25)$ \\ 
			\hline 
			& $1.0e-4$    & 692 & 371  & 350   & 171   & 65    \\ 
			& $1.8e-4$    & 744 & 367  & 220   & 150   & 55    \\   
			$T=0.5$ & $3.2e-4$    & 805 & 364  & 271   & 164   & 51    \\ 
			& $5.6e-4$    & 867 & 365  & 400   & 171   & 45    \\  
			& $1.0e-3$    & 820 & 383  & 139   & 82   & 37    \\ 
			\hline
			& $1.0e-4$    & 744 & 526  & 620   & 338   & 108    \\ 
			& $1.8e-4$    & 769 & 528  & 554   & 248   & 98    \\   
			$T=1.0$ & $3.2e-4$    & 778 & 542  & 401   & 233   & 101    \\ 
			& $5.6e-4$    & 725 & 570  & 296   & 227   & 80    \\  
			& $1.0e-3$    & 666 & 624  & 299   & 291   & 251    \\ 
			\hline
			& $1.0e-4$    & 718 & 707  & 616   & 596   & 194    \\ 
			& $1.8e-4$    & 670 & 731  & 505   & 478   & 207    \\   
			$T=2.0$ & $3.2e-4$    & 606 & 778  & 382   & 445   & 189    \\ 
			& $5.6e-4$    & 528 & 856  & 558   & 326   & 173    \\  
			& $1.0e-3$    & 398 & 945  & 425   & 294   & 182    \\ 
		\end{tabular}
		\endgroup
	\end{center}
	\caption{Number of preconditioned conjugate gradient iterations to achieve tolerance $10^{-7}$ for solving the Newton linear system in the advection-diffusion inverse problem. Iteration counts are shown for a variety of different diffusion parameters $\kappa$, simulation times $T$, and preconditioners.}
	\label{tab:adv_convergence}
\end{figure}
